Sparse spectral methods for partial differential equations on spherical caps

### 2020-10-26 papers/spherical-caps/spherical-caps.tex
Finish proof read

For the operator $D_\theta$ for partial differentiation by $\theta$, we simply have that
\begin{align*}
	\pptheta \scopnkia(x,y,z) &= \genjacnmk^{(a,2k)}(z) \: \rho(z)^{k} \: \ddx{\theta} \chki(\theta) \\
	&= 
	\begin{cases}
		(-1)^{i+1} \: k \: \scopa_{n,k,|i-1|}(x,y,z) & k > 0 \\
		0 & k = 0
	\end{cases}
\end{align*}

We now proceed with the case for the operator $D_\varphi^{(a)}$ for partial differentiation by $\varphi$. The entries of the operator are given by the coefficients in the expansion $\rhoppphi \scopnkia = \sum_{m=0}^{n+1} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j,h} \: \scopmjh^{(a+1)}$, where the coefficients are 
\begin{align*}
	c_{m,j,h} = \norm{\scopmjh^{(a+1)}}^{-2}_{\scop^{(a+1)}} \ip<\rhoppphi \scopnkia, \: \scopmjh^{(a+1)}>_{\scop^{(a+1)}}.
\end{align*}
Now, note that:
\begin{align*}
	\genjacw^{(a,b) \: \prime}(z) &= a \: \genjacw^{(a-1,b)}(z) + c \: \rho(z) \: \rho'(z) \:\genjacw^{(a,b-2)}(z), \\
	\rho(z) \: \rho'(z) &= -z \\
	\ppphi \scopnkia(x,y,z) &= -\rho(z) \: \ddz \Big[ \rho(z)^k \: \genjacnmk^{(a,2k)}(z) \Big] \chki(\theta), \\
	\ppphi \Big[ \genjacw^{(a,0)}(z) \: \scopnkia(x,y,z) \Big] &= -\rho(z) \: \ddz \Big[ \genjacw^{(a,k)}(z) \: \genjacnmk^{(a,2k)}(z) \Big] \chki(\theta).
\end{align*}
Then, 
\begin{align*}
	&\ip<\rhoppphi \scopnkia, \: \scopmjh^{(a+1)}>_{\scop^{(a+1)}} \\
	&\quad = - \int_\alpha^1 \Big( \int_0^{2\pi} \: \rho(z)^2 \ddz \: [\genjacnmk^{(a,2k)}(z) \: \rho(z)^k] \: \genjacmmj^{(a+1,2j)}(z) \: \rho(z)^j \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \: \genjacw^{(a+1, 0)} \: \D z \\
	&\quad = \Big( \int_0^{2\pi} \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \: \Big( \int_\alpha^1 \: \genjacmmj^{(a+1,2j)} \: [k z \genjacnmk^{(a, 2k)} - \rho^2 \genjacnmk^{(a, 2k) \: \prime}] \: \genjacw^{(a+1, k + j)} \: \D z \Big) \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjac_{m-k}^{(a+1,2k)} \: [k z \genjacnmk^{(a, 2k)} - \rho^2 \genjacnmk^{(a, 2k) \: \prime}] \: \genjacw^{(a+1, 2k)} \: \D z \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjacnmk^{(a, 2k)} \: \Big\{  k z \: \genjac_{m-k}^{(a+1,2k)} \: \genjacw^{(1, 0)} + \genjac_{m-k}^{(a+1,2k) \: \prime} \: \genjacw^{(1, 2)}\\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + a \: \rho^2 \: \genjac_{m-k}^{(a+1,2k)} - (2k+2) z \: \genjac_{m-k}^{(a+1,2k)} \: \genjacw^{(1, 0)} \Big\} \: \genjacw^{(a, 2k)} \: \D z
\end{align*}
which is zero for $j \ne k$, $h \ne i$, and $m < n - 2$ by orthogonality.

@@

We move onto the spherical Laplacian operators. Note that the Laplacian acting on the weighted and non-weighted spherical cap OP $\scopnki^{(a)}$ yields
\begin{align}
	\DeltaS \: \scopnki^{(a)} &= {1 \over \rho} \ppx{\varphi} \Big( \rho \ppx{\varphi} [\genjacnmk^{(a,2k)}(\cosphi) \: \sin^k\varphi] \Big) \chki(\theta) \nonumber \\
	&\quad \quad \quad \quad + \genjacnmk^{(a,2k)}(\cosphi) \: \sin^{k-2}\varphi \pmpxm{\theta}{2} \chki(\theta) \nonumber \\
	&= \chki(\theta) \rho(z)^k \Big\{ -k(k+1) \genjacnmk^{(a,2k)}(z) - 2(k+1) z \: \genjacnmk^{(a,2k) \: \prime}(z) \nonumber \\
	&\quad \quad \quad \quad \quad \quad \quad + \rho(z)^2 \genjacnmk^{(a,2k) \: \prime \prime}(z) \Big\}, \label{eqn:oplaplacian} \\
	\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big) &= {1 \over \rho} \ppx{\varphi} \Big( \rho \ppx{\varphi} [\genjacw^{(a,0)}(\cosphi) \: \genjacnmk^{(a,2k)}(\cosphi) \: \sin^k\varphi] \Big) \chki(\theta) \nonumber \\
	&\quad \quad \quad \quad + \genjacw^{(a,0)}(\cosphi) \: \genjacnmk^{(a,2k)}(\cosphi) \: \sin^{k-2}\varphi \pmpxm{\theta}{2} \chki(\theta) \nonumber \\
	&= \chki(\theta) \Big\{\genjacnmk^{(a,2k)}(z) \big[ -k(k+1) \genjacw^{(a,k)}(z) - 2a(k+1) z \: \genjacw^{(a-1,k)}(z) \big] \nonumber \\
	&\quad \quad \quad \quad \quad + a(a-1) \genjacnmk^{(a,2k)}(z) \: \genjacw^{(a-2,k+1)}(z) \nonumber \\
	&\quad \quad \quad \quad \quad + \genjacnmk^{(a,2k) \: \prime}(z) \big[ -2(k+1) z \: \genjacw^{(a,k)}(z) + 2a \: \genjacw^{(a-1,k+2)}(z) \big] \nonumber \\
	&\quad \quad \quad \quad \quad + \genjacnmk^{(a,2k) \: \prime \prime}(z) \: \genjacw^{(a,k+2)}(z) \Big\}. \label{eqn:woplaplacian}
\end{align}

For the operator $\calL^{(a)\to(a+\tilde a)}$ for the surface Laplacian on a non-weighted space, the entries of the operator are given by the coefficients in the expansion $\DeltaS \scopnki^{(a)} = \sum_{m=0}^{n} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j,h} \: \scopmjh^{(a + \tilde a)}$, where the coefficients are
\begin{align*}
	c_{m,j,h} = \norm{\scopmjh^{(a + \tilde a)}}^{-2}_{\scop^{(a + \tilde a)}} \ip<\DeltaS \scopnki^{(a)}, \: \scopmjh^{(a + \tilde a)}>_{\scop^{(a + \tilde a)}}.
\end{align*}
Using \bsrefeqn{eqn:oplaplacian}, and integrating by parts twice, we then have that
\begin{align*}
	&\ip<\DeltaS \scopnki^{(a)}, \: \scopmjh^{(a + \tilde a)}>_{\scop^{(a + \tilde a)}} \\
	&\quad = \Big( \int_0^{2\pi} \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \\
	&\quad \quad \quad \quad \cdot \: \Big( \int_\alpha^1 \: \genjacmmj^{(a + \tilde a, 2j)} \: \genjacw^{(a + \tilde a), k+j)} \: \Big\{-k(k+1) \genjacnmk^{(a,2k)} - 2(k+1) z \: \genjacnmk^{(a,2k) \: \prime} \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + \rho(z)^2 \genjacnmk^{(a,2k) \: \prime \prime} \Big\} \: \D z \Big) \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjac_{m-k}^{(a+\tilde a,2k)} \: \genjacw^{(a+\tilde a, 0)} \Big( -k(k+1) \genjacnmk^{(a,2k)} \: \rho^{2k} + \ddx{z} [\genjacnmk^{(a,2k) \: \prime} \: \rho^{2(k+1)}] \Big) \: \D z \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ -k(k+1) \genjac_{m-k}^{(a+\tilde a,2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a+\tilde a, 2k)} \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad - \genjacnmk^{(a,2k) \: \prime} \genjacw^{(a+\tilde a-1, 2k)} \: [\genjac_{m-k}^{(a+\tilde a,2k) \: \prime} \: \genjacw^{(1,0)} + (a + \tilde a) \genjac_{m-k}^{(a+\tilde a,2k)}] \Big\} \: \D z \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjacnmk^{(a,2k)} \: \genjacw^{(a, 2k)} \: r_{m-k+\tilde a} \: \D z
\end{align*}
where $r_{m-k+\tilde a}$ is a degree $m - k + \tilde a$ polynomial in $z$, and so the above is zero for $n  - k > m - k + \tilde a \iff m < n - \tilde a$.

@@

\begin{definition}\label{def:parametertransformationoperators}
Define the operator matrices $T^{(a)\to(a+\tilde a)}, \quad T^{(a)\to(a-\tilde a)}$ for conversion between non-weighted spaces and weighted spaces respectively according to
\begin{align*}
	\bigscopNa(x,y,z) &= \Big(T^{(a)\to(a+\tilde a)} \Big)^\top \: \bigscopN^{(a+\tilde a)}(x,y,z) \\
	\bigWNa(x,y,z) &= \Big(T_W^{(a)\to(a-\tilde a)} \Big)^\top \: \bigW_N^{(a-\tilde a)}(x,y,z)
\end{align*}
\end{definition}

@@

	\medskip
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[scale=0.3]{sparsity-of-helmholtz}
		\centering
		\caption{A variable coefficient Helmholtz operator}
	\end{subfigure}\hfil % <-- added
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[scale=0.23]{sparsity-of-biharmonic}
		\centering
		\caption{The Biharmonic operator $B_W^{(2)}$} 
	\end{subfigure}\hfil % <-- added
	\caption{\enquote{Spy} plots of (differential) operator matrices, showing their sparsity. For (c), the the weighted variable coefficient Helmholtz operator is $\Delta^{(1)}_W + k^2 \: T^{(0)\to(1)} \: V({J_x^{(0)}}^\top, {J_y^{(0)}}^\top, {J_z^{(0)}}^\top) \: T_W^{(1)\to(0)}$ for $v(x,y,z) = 1 - (3(x-x_0)^2 + 5(y-y_0)^2 + 2(z-z_0)^2)$ where $(x_0, z_0) := (0.7, 0.2)$, $y_0 := \sqrt{(x_0^2 + z_0^2)}$ and $k = 200$.}
	\label{fig:sparsity}
\end{figure}

@@

For a function $f$, with coefficients vector $\bm{f}$ for expansion in the $\{\scopnki\}$ basis as determined via the method in Section \ref{subsection:expandingfunctions} up to order $N$, we can use the Clenshaw algorithm to evaluate the function at a point $(x,y,z) \in \Omega$ as follows. Let $A_n, B_n, \Dnt, C_n$ be the Clenshaw matrices from Definition \ref{def:clenshawmats}, and define the rearranged coefficients vector $\tilde{\bm{f}}$ via
\begin{align*}
	\tilde{\bm{f}}_n &:= 
		\begin{pmatrix}
			f_{n,0,0} \\
			f_{n,1,0} \\
			f_{n,1,1} \\
			\vdots \\
			f_{n,n,0} \\
			f_{n,n,1}
		\end{pmatrix} \in \R^{2(N+1)} \quad \text{for } n = 1,2,\dots,N, \quad
	\tilde{\bm{f}}_0 = f_{0,0,0} \in \R, \\
	\tilde{\bm{f}} &:= 
		\begin{pmatrix}
			\tilde{\bm{f}}_0 \\
			\vdots \\
			\tilde{\bm{f}}_N
		\end{pmatrix} \in \R^{(N+1)^2}.
\end{align*}
The trivariate Clenshaw algorithm works similar to the bivariate Clenshaw algorithm introduced in \cite{olver2019triangle}:
\begin{align*}
	\quad &\text{1) } \text{Set } \bm{\xi}_{N+2} = \bold{0}, \: \bm{\xi}_{N+2} = \bold{0}. \\
	\quad &\text{2) } \text{For } n = N:-1:0 \\
	\quad & \quad \quad \quad \text{set } \bm{\xi}_{n}^T = {\tilde{\bm{f}}_n}^T - \bm{\xi}_{n+1}^T D^T_n (B_n - G_n(x,y,z)) -  \bm{\xi}_{n+2}^T D^T_{n+1}C_{n+1} \\
	\quad &\text{3) } \text{Output: } f(x,y,z) \approx \bm{\xi}_{0} \: \bigscopta_{0}  = \xi_{0} \: \scopa_0
\end{align*}

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.25]{poisson-u=wyexpx-N=60}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.3]{solutionblocknorms-poisson-epsilonfun-N=200}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y,z) = - 2 e^x y z (2+x) + \genjacw^{(1,0)}(z) e^x (y^3 + z^2 y - 4xy - 2y)$. Right: The norms of each block of the computed solution of the Poisson equation with right hand side function $f(x,y,z) = \norm{\xvec - (\epsilon + 1 / \sqrt{3}) \; (1,1,1)^\top }$ for different $\epsilon$ values. This demonstrates spectral convergence observed.
	\bstodoinline{New solution block norms plots. I have only gone up to N=100 (200 for Poisson) for now, mainly because expanding a RHS function f for larger N takes a looong time, which is where we would see the benefit of a higher N plot (for the simpler $f$'s, we would just see more super convergence).}}
	\centering
	\label{fig:poisson}
\end{figure}
%
%\begin{figure}[t]
%	\begin{subfigure}{0.3\textwidth}
%	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx}
%	\centering
%	\end{subfigure}
%	\begin{subfigure}{0.3\textwidth}
%	\centering
%	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-actual}
%	\centering
%	\end{subfigure}
%	\begin{subfigure}{0.3\textwidth}
%	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-compare}
%	\centering
%	\end{subfigure}
%	\centering
%	\caption{The computed solution to $\Delta u = f$ with zero boundary conditions compared with the exact solution $u(x,y) = \Wiii (x,y) y^3 \exp(x)$. Left: Computed. Centre: Exact. Right: Plot of the error (colourbar is shown to demonstrate magnitude of the error is of the order $10^{-17}$)}
%	\centering
%	\label{fig:poissonexact}
%\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.25]{helmholtz-f=wyexpx-N=60-n=300}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.3]{solutionblocknorms-helmholtz-varyingk-N=100}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y,z) = y e^x (z - \alpha) $, $v(x,y,z) = 1 - (3(x-x_0)^2 + 5(y-y_0)^2 + 2(z-z_0)^2)$ where $(x_0, z_0) := (0.7, 0.2)$, $y_0 := \sqrt{(x_0^2 + z_0^2)}$ and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the right hand side function $f(x,y,z) = 1$ and the same function $v(x,y,z)$, for various $k$ values. This demonstrates spectral convergence observed.}
	\centering
	\label{fig:helmholtz}
\end{figure}

>>>>

For the operator $D_\theta$ for partial differentiation by $\theta$, we simply have that
\begin{align*}
	\pptheta \scopnkia(x,y,z) &= \genjacnmk^{(a,2k)}(z) \: \rho(z)^{k} \: \ddx{\theta} \chki(\theta) \\
	&= 
	\begin{cases}
		(-1)^{i+1} \: k \: \scopa_{n,k,|i-1|}(x,y,z) & k > 0 \\
		0 & k = 0
	\end{cases}.
\end{align*}

We now proceed with the case for the operator $D_\varphi^{(a)}$ for partial differentiation by $\varphi$. The entries of the operator are given by the coefficients in the expansion 
$$
\rhoppphi \scopnkia = \sum_{m=0}^{n+1} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j,h} \: \scopmjh^{(a+1)},
$$ 
where the coefficients are 
\begin{align*}
	c_{m,j,h} = \norm{\scopmjh^{(a+1)}}^{-2}_{\scop^{(a+1)}} \ip<\rhoppphi \scopnkia, \: \scopmjh^{(a+1)}>_{\scop^{(a+1)}}.
\end{align*}
Now, note that:
\begin{align*}
	\genjacw^{(a,b) \: \prime}(z) &= a \: \genjacw^{(a-1,b)}(z) + c \: \rho(z) \: \rho'(z) \:\genjacw^{(a,b-2)}(z), \\
	\rho(z) \: \rho'(z) &= -z \\
	\ppphi \scopnkia(x,y,z) &= -\rho(z) \: \ddz \Big[ \rho(z)^k \: \genjacnmk^{(a,2k)}(z) \Big] \chki(\theta), \\
	\ppphi \Big[ \genjacw^{(a,0)}(z) \: \scopnkia(x,y,z) \Big] &= -\rho(z) \: \ddz \Big[ \genjacw^{(a,k)}(z) \: \genjacnmk^{(a,2k)}(z) \Big] \chki(\theta).
\end{align*}
Then, 
\begin{align*}
	&\ip<\rhoppphi \scopnkia, \: \scopmjh^{(a+1)}>_{\scop^{(a+1)}} \\
	&\quad = - \int_\alpha^1 \Big( \int_0^{2\pi} \: \rho(z)^2 \ddz \: [\genjacnmk^{(a,2k)}(z) \: \rho(z)^k] \: \genjacmmj^{(a+1,2j)}(z) \: \rho(z)^j \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \: \genjacw^{(a+1, 0)} \: \D z \\
	&\quad = \Big( \int_0^{2\pi} \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \: \Big( \int_\alpha^1 \: \genjacmmj^{(a+1,2j)} \: [k z \genjacnmk^{(a, 2k)} - \rho^2 \genjacnmk^{(a, 2k) \: \prime}] \: \genjacw^{(a+1, k + j)} \: \D z \Big) \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjac_{m-k}^{(a+1,2k)} \: [k z \genjacnmk^{(a, 2k)} - \rho^2 \genjacnmk^{(a, 2k) \: \prime}] \: \genjacw^{(a+1, 2k)} \: \D z \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjacnmk^{(a, 2k)} \: \Big\{  k z \: \genjac_{m-k}^{(a+1,2k)} \: \genjacw^{(1, 0)} + \genjac_{m-k}^{(a+1,2k) \: \prime} \: \genjacw^{(1, 2)}\\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + a \: \rho^2 \: \genjac_{m-k}^{(a+1,2k)} - (2k+2) z \: \genjac_{m-k}^{(a+1,2k)} \: \genjacw^{(1, 0)} \Big\} \: \genjacw^{(a, 2k)} \: \D z
\end{align*}
which is zero for $j \ne k$, $h \ne i$, and $m < n - 2$ by orthogonality.

@@

We move on to the spherical Laplacian operators. Note that the Laplacian acting on the weighted and non-weighted spherical cap OP $\scopnki^{(a)}$ yield
\begin{align}
	\DeltaS \: \scopnki^{(a)} &= {1 \over \rho} \ppx{\varphi} \Big( \rho \ppx{\varphi} [\genjacnmk^{(a,2k)}(\cosphi) \: \sin^k\varphi] \Big) \chki(\theta) \nonumber \\
	&\quad \quad \quad \quad + \genjacnmk^{(a,2k)}(\cosphi) \: \sin^{k-2}\varphi \pmpxm{\theta}{2} \chki(\theta) \nonumber \\
	&= \chki(\theta) \rho(z)^k \Big\{ -k(k+1) \genjacnmk^{(a,2k)}(z) - 2(k+1) z \: \genjacnmk^{(a,2k) \: \prime}(z) \nonumber \\
	&\quad \quad \quad \quad \quad \quad \quad + \rho(z)^2 \genjacnmk^{(a,2k) \: \prime \prime}(z) \Big\}, \label{eqn:oplaplacian} \\
	\DeltaS \big(\genjacw^{(a,0)} \: \scopnki^{(a)} \big) &= {1 \over \rho} \ppx{\varphi} \Big( \rho \ppx{\varphi} [\genjacw^{(a,0)}(\cosphi) \: \genjacnmk^{(a,2k)}(\cosphi) \: \sin^k\varphi] \Big) \chki(\theta) \nonumber \\
	&\quad \quad \quad \quad + \genjacw^{(a,0)}(\cosphi) \: \genjacnmk^{(a,2k)}(\cosphi) \: \sin^{k-2}\varphi \pmpxm{\theta}{2} \chki(\theta) \nonumber \\
	&= \chki(\theta) \Big\{\genjacnmk^{(a,2k)}(z) \big[ -k(k+1) \genjacw^{(a,k)}(z) - 2a(k+1) z \: \genjacw^{(a-1,k)}(z) \big] \nonumber \\
	&\quad \quad \quad \quad \quad + a(a-1) \genjacnmk^{(a,2k)}(z) \: \genjacw^{(a-2,k+1)}(z) \nonumber \\
	&\quad \quad \quad \quad \quad + \genjacnmk^{(a,2k) \: \prime}(z) \big[ -2(k+1) z \: \genjacw^{(a,k)}(z) + 2a \: \genjacw^{(a-1,k+2)}(z) \big] \nonumber \\
	&\quad \quad \quad \quad \quad + \genjacnmk^{(a,2k) \: \prime \prime}(z) \: \genjacw^{(a,k+2)}(z) \Big\}. \label{eqn:woplaplacian}
\end{align}

For the operator $\calL^{(a)\to(a+\tilde a)}$ for the surface Laplacian on a non-weighted space, the entries of the operator are given by the coefficients in the expansion 
$$\DeltaS \scopnki^{(a)} = \sum_{m=0}^{n} \sum_{j=0}^m \sum_{h=0}^1 c_{m,j,h} \: \scopmjh^{(a + \tilde a)},$$
 where the coefficients are
\begin{align*}
	c_{m,j,h} = \norm{\scopmjh^{(a + \tilde a)}}^{-2}_{\scop^{(a + \tilde a)}} \ip<\DeltaS \scopnki^{(a)}, \: \scopmjh^{(a + \tilde a)}>_{\scop^{(a + \tilde a)}}.
\end{align*}
Using \bsrefeqn{eqn:oplaplacian}, and integrating by parts twice, we then have that
\begin{align*}
	&\ip<\DeltaS \scopnki^{(a)}, \: \scopmjh^{(a + \tilde a)}>_{\scop^{(a + \tilde a)}} \\
	&\quad = \Big( \int_0^{2\pi} \: \chki(\theta) \: \chjh(\theta) \: \D \theta \Big) \\
	&\quad \quad \quad \quad \cdot \: \Big( \int_\alpha^1 \: \genjacmmj^{(a + \tilde a, 2j)} \: \genjacw^{(a + \tilde a), k+j)} \: \Big\{-k(k+1) \genjacnmk^{(a,2k)} - 2(k+1) z \: \genjacnmk^{(a,2k) \: \prime} \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad + \rho(z)^2 \genjacnmk^{(a,2k) \: \prime \prime} \Big\} \: \D z \Big) \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjac_{m-k}^{(a+\tilde a,2k)} \: \genjacw^{(a+\tilde a, 0)} \Big( -k(k+1) \genjacnmk^{(a,2k)} \: \rho^{2k} + \ddx{z} [\genjacnmk^{(a,2k) \: \prime} \: \rho^{2(k+1)}] \Big) \: \D z \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \Big\{ -k(k+1) \genjac_{m-k}^{(a+\tilde a,2k)} \: \genjacnmk^{(a,2k)} \: \genjacw^{(a+\tilde a, 2k)} \\
	&\quad \quad \quad \quad \quad \quad \quad \quad \quad \quad - \genjacnmk^{(a,2k) \: \prime} \genjacw^{(a+\tilde a-1, 2k)} \: [\genjac_{m-k}^{(a+\tilde a,2k) \: \prime} \: \genjacw^{(1,0)} + (a + \tilde a) \genjac_{m-k}^{(a+\tilde a,2k)}] \Big\} \: \D z \\
	&\quad = \pi \: \delta_{k,j} \: \delta_{i,h} \: \int_\alpha^1 \: \genjacnmk^{(a,2k)} \: \genjacw^{(a, 2k)} \: r_{m-k+\tilde a} \: \D z
\end{align*}
where $r_{m-k+\tilde a}$ is a degree $m - k + \tilde a$ polynomial in $z$, and so the above is zero for $n  - k > m - k + \tilde a \iff m < n - \tilde a$.

@@

\begin{definition}\label{def:parametertransformationoperators}
Define the operator matrices $T^{(a)\to(a+\tilde a)}, \quad T_W^{(a)\to(a-\tilde a)}$ for conversion between non-weighted spaces and weighted spaces respectively according to
\begin{align*}
	\bigscopNa(x,y,z) &= \Big(T^{(a)\to(a+\tilde a)} \Big)^\top \: \bigscopN^{(a+\tilde a)}(x,y,z) \\
	\bigWNa(x,y,z) &= \Big(T_W^{(a)\to(a-\tilde a)} \Big)^\top \: \bigW_N^{(a-\tilde a)}(x,y,z)
\end{align*}
\end{definition}

@@

	\medskip
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[scale=0.3]{sparsity-of-helmholtz}
		\centering
		\caption{A variable coefficient Helmholtz operator}
	\end{subfigure}\hfil % <-- added
	\begin{subfigure}{0.45\textwidth}
		\includegraphics[scale=0.23]{sparsity-of-biharmonic}
		\centering
		\caption{The Biharmonic operator $B_W^{(2)}$} 
	\end{subfigure}\hfil % <-- added
	\caption{\enquote{Spy} plots of (differential) operator matrices, showing their sparsity. For (c), the the weighted variable coefficient Helmholtz operator is $\Delta^{(1)}_W + k^2 \: T^{(0)\to(1)} \: V({J_x^{(0)}}^\top, {J_y^{(0)}}^\top, {J_z^{(0)}}^\top) \: T_W^{(1)\to(0)}$ for $v(x,y,z) = 1 - (3(x-x_0)^2 + 5(y-y_0)^2 + 2(z-z_0)^2)$ where $(x_0, z_0) := (0.7, 0.2)$, $y_0 := \sqrt{(x_0^2 + z_0^2)}$ \sotodoinline{Shouldn't this be $\sqrt{1-x_0^2-y_0^2}$?} and $k = 200$.}
	\label{fig:sparsity}
\end{figure}

@@

For a function $f$, with coefficients vector $\bm{f}$ for expansion in the $\{\scopnki\}$ basis as determined via the method in Section \ref{subsection:expandingfunctions} up to order $N$, we can use the Clenshaw algorithm to evaluate the function at a point $(x,y,z) \in \Omega$ as follows. Let $A_n, B_n, \Dnt, C_n$ be the Clenshaw matrices from Definition \ref{def:clenshawmats}, and define the rearranged coefficients vector $\tilde{\bm{f}}$ via
\begin{align*}
	\tilde{\bm{f}}_n &:= 
		\begin{pmatrix}
			f_{n,0,0} \\
			f_{n,1,0} \\
			f_{n,1,1} \\
			\vdots \\
			f_{n,n,0} \\
			f_{n,n,1}
		\end{pmatrix} \in \R^{2(N+1)} \quad \text{for } n = 1,2,\dots,N, \quad
	\tilde{\bm{f}}_0 = f_{0,0,0} \in \R, \\
	\tilde{\bm{f}} &:= 
		\begin{pmatrix}
			\tilde{\bm{f}}_0 \\
			\vdots \\
			\tilde{\bm{f}}_N
		\end{pmatrix} \in \R^{(N+1)^2}.
\end{align*}
The trivariate Clenshaw algorithm works similar to the bivariate Clenshaw algorithm introduced in \cite{olver2019triangle} for expansions in the triangle:
\begin{align*}
	\quad &\text{1) } \text{Set } \bm{\xi}_{N+2} = \bold{0}, \: \bm{\xi}_{N+2} = \bold{0}. \\
	\quad &\text{2) } \text{For } n = N:-1:0 \\
	\quad & \quad \quad \quad \text{set } \bm{\xi}_{n}^T = {\tilde{\bm{f}}_n}^T - \bm{\xi}_{n+1}^T D^T_n (B_n - G_n(x,y,z)) -  \bm{\xi}_{n+2}^T D^T_{n+1}C_{n+1} \\
	\quad &\text{3) } \text{Output: } f(x,y,z) \approx \bm{\xi}_{0} \: \bigscopta_{0}  = \xi_{0} \: \scopa_0
\end{align*}

@@

% FIGURES
\begin{figure}[t]
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.25]{poisson-u=wyexpx-N=60}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.3]{solutionblocknorms-poisson-epsilonfun-N=200}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u = f$ with zero boundary conditions with $f(x,y,z) = - 2 e^x y z (2+x) + \genjacw^{(1,0)}(z) e^x (y^3 + z^2 y - 4xy - 2y)$. Right: The norms of each block of the computed solution of the Poisson equation with right hand side function $f(x,y,z) = \norm{\xvec - (\epsilon + 1 / \sqrt{3}) \; (1,1,1)^\top }$ for different $\epsilon$ values. This indicates spectral convergence.}
	\centering
	\label{fig:poisson}
\end{figure}
%
%\begin{figure}[t]
%	\begin{subfigure}{0.3\textwidth}
%	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx}
%	\centering
%	\end{subfigure}
%	\begin{subfigure}{0.3\textwidth}
%	\centering
%	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-actual}
%	\centering
%	\end{subfigure}
%	\begin{subfigure}{0.3\textwidth}
%	\includegraphics[scale=0.3]{solution-exact-poisson-diskslice-alpha=0p2-beta=0p8-u=y3expx-compare}
%	\centering
%	\end{subfigure}
%	\centering
%	\caption{The computed solution to $\Delta u = f$ with zero boundary conditions compared with the exact solution $u(x,y) = \Wiii (x,y) y^3 \exp(x)$. Left: Computed. Centre: Exact. Right: Plot of the error (colourbar is shown to demonstrate magnitude of the error is of the order $10^{-17}$)}
%	\centering
%	\label{fig:poissonexact}
%\end{figure}

\begin{figure}[t]
	\begin{subfigure}{0.5\textwidth}
	\includegraphics[scale=0.25]{helmholtz-f=wyexpx-N=60-n=300}
	\centering
	%\label{fig:solution-poisson}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.3]{solutionblocknorms-helmholtz-varyingk-N=100}
        	%\label{fig:solutionblocknorms-poisson}
	\end{subfigure}
	\caption{Left: The computed solution to $\Delta u + k^2 \: v \: u = f$ with zero boundary conditions with $f(x,y,z) = y e^x (z - \alpha) $, $v(x,y,z) = 1 - (3(x-x_0)^2 + 5(y-y_0)^2 + 2(z-z_0)^2)$ where $(x_0, z_0) := (0.7, 0.2)$, $y_0 := \sqrt{(x_0^2 + z_0^2)}$ \sotodoinline{Here too} and $k = 100$. Right: The norms of each block of the computed solution of the Helmholtz equation with the right hand side function $f(x,y,z) = 1$ and the same function $v(x,y,z)$, for various $k$ values. This indicates spectral convergence. \sotodoinline{Since this example has simple right-hand side, wouldn't it be easy to extend to $N = 200$?}}
	\centering
	\label{fig:helmholtz}
\end{figure}
